
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
% \raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Vineet Kekatpure} \\ \vspace{1pt}
    \small +91-7021312855 $|$ \href{mailto:vineet.kekatpure@gmail.com}{vineet.kekatpure@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/vineet-kekatpure}{linkedin.com/in/vineet-kekatpure}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  \small{Results-driven Software Engineer II and Scrum Master with over 3 years of experience in the cybersecurity domain at Forcepoint. Expert in balancing technical execution with Agile leadership, overseeing high-velocity delivery for the DLP Engine team. Proven track record in modernizing legacy systems, automating developer workflows, and engineering core C++ security components.}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Forcepoint}{Thane, India}
      {Software Engineer II}{July 2022 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Core Engineering \& Development}}
        \resumeItemListStart
            \resumeItem{\textbf{Core Security Features}: Engineered a custom algorithm for 'Random Text Extraction' and developed C++ filetype classifiers for the core DLP engine.}
            \resumeItem{\textbf{Legacy Modernization}: Led a 10-year refresh of critical external libraries to fix long-standing security gaps and update the system.}
            \resumeItem{\textbf{System Rewrite}: Managed the architectural move from legacy Python 2 to Python 3 for the DLP FSM System Health to make the system up to date and modern.}
            \resumeItem{\textbf{Critical Fixes}: Handled high-priority ``fastrack'' escalations and fixed major bugs to keep the security engine running smoothly.}
        \resumeItemListEnd
        
        \resumeItem{\textbf{Agile Leadership \& Delivery}}
        \resumeItemListStart
            \resumeItem{\textbf{Scrum Leadership}: Orchestrate all Scrum ceremonies, including PI Planning and Capacity Planning, Daily Standups, Sprint Planning, and Retrospectives for the DLP Engine team to ensure roadmap alignment.}
            \resumeItem{\textbf{Predictable Velocity}: My scrum consistently achieved a 75\% average completion rate for committed initiatives per PI in an Agile environment.}
            \resumeItem{\textbf{Process Optimization}: Designed and deployed a custom Python automation script that reduced the time spent by developers on Jira ticket administration by approximately 90\% across the organization.}
        \resumeItemListEnd
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C++, Python.} \\
     \textbf{Core Technical}{: Data Structures \& Algorithms (DSA), Object-Oriented Programming (OOP), System Architecture, Code Optimization, Debugging, Legacy Code Modernization, Technical Debt Mitigation} \\
     \textbf{Tools \& Platforms}{: Visual Studio, Git, Perforce, Makefiles, Jira.} \\
     \textbf{Agile Leadership}{: Scrum Master, PI Planning, Capacity Planning, Retrospectives.}
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fr. Conceicao Rodrigues Institute of Technology, Vashi}{Mumbai University}
      {Bachelor of Engineering in Information Technology (8.37 CGPI)}{2018 -- 2022}
  \resumeSubHeadingListEnd


%-----------VOLUNTEERING-----------
\section{Volunteering}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fr. Conceicao Rodrigues Institute of Technology}{Mumbai University}
      {Member, Board of Studies}{April 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Collaborated with experts from education and tech on the strategic design of academic syllabi, including the selection of subjects, modules, and laboratory curriculum.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeItem{\faLink~ \href{https://www.udemy.com/certificate/UC-a0a0912b-9347-4923-aca7-90fdb0d2d7ac/}{\textbf{Agile Scrum for Beginners + Scrum Master Certification PSM 1}} (Udemy, Oct 2024)}
  \resumeSubHeadingListEnd



%-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Spoken}{: English, Hindi, Marathi}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
